Looking for CDI Bias: WG Comprehension

### 2021-08-11 02-preliminary-WGcomp.Rmd
production (WS only) glimmer plots

```{r get-wordbank-items, eval=F, echo=F}
d_long_wg <- get_instrument_data(language="English (American)", form = "WG") %>%
  mutate(understands = as.numeric(value == "yes" | value == "produces" | value == "understands")) # we'll start with production
# yes = understands; no = does not understand/produce, produces = produces (and understands)

>>>>

```{r get-wordbank-items, eval=F, echo=F}
d_long_wg <- get_instrument_data(language="English (American)", form = "WG") %>%
  mutate(understands = as.numeric(value == "yes" | value == "produces" | value == "understands")) # we'll start with comprehension
# yes = understands; no = does not understand/produce, produces = produces (and understands)
